Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-05-19 manuscript/Chapter3-manuscript.Rmd
start paragraph 2 of intro

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016]. Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015:@Phillips.etal2017]. It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@bolnickEcologyIndividualsIncidence2003;@bolnickWhyIntraspecificTrait2011]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016]. For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to learn through experience how to effectively use them is essential to maintain foraging success. Yet, we have very limited knowledge on how predator foraging specialization develops through experience and interactions with prey, and the resulting ecological consequences of such among individual behavioural differences for predator-prey interactions [@Phillips.etal2017].

Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources]. Learning how to hunt is crucial for young predators to reach adulthood and survive. (check Urszan et al)
(learning optimises return rates or foraging success)
(apprentissage, search images, prior information)
(par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
(parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)
[*références learning : phillips, Haage(minks), Tinker (théorique), Weimerskirch ()*]

A number of long-term studies observed that generalist and specialist individuals can achieve similar fitness [sources: à partir de Woo]. An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc, Courbin, Chang]. The resource-predictability hypothesis advances that when resources are predictable, particularly on short time-scales, individual specialists should benefit from higher fitness returns. The rationale is that individuals should have higher prey delivery rates when they repeatedly employ the same foraging technique, as it is easier to assess prey predictability over shorter time-scales. In contrast, individual generalists should be advantaged over longer time scales, as resource parameters are expected to fluctuate. [revoir ceia et ramos pour les sources]

>>>>

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016]. Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017]. It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@bolnickEcologyIndividualsIncidence2003;@bolnickWhyIntraspecificTrait2011]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016]. For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to learn through experience how to effectively use them is essential to maintain foraging success. Yet, we have very limited knowledge on how predator foraging specialization develops through experience and interactions with prey, and the resulting ecological consequences of such among individual behavioural differences for predator-prey interactions.

Learning how to hunt prey is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@heithausFeedingStrategiesTactics2018]. Theory predicts that specialization through learning may result from past experiences in handling prey as well as a limited ability to retain complex learned skills for multiple prey types [@Tinker.etal2009]. Empirical studies shows that learning can optimize the efficiency of foraging strategies (e.g. search and handling times, return rates) potentially via associative images or increased reliance on prey and environmental cues [@edwardsRoleExperienceDevelopment1994;@morseEffectExperienceHunting2000;@reidLearningHuntRole2010;@wilson-rankinLevelExperienceModulates2015]. While this does not directly indicate foraging specialization, such optimization may reinforce the use of the same strategy (i.e. specialization) if its success is constant through repeated attempts. *parler des couts d'apprendre de quoi d'autre*

*expliquer comment ça optimise*
*expliquer comment ça peut mener aussi à de la plasticité*
*parler des coûts*

(apprentissage, search images, prior information)
(par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
(parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)
[*références learning : phillips, Haage(minks = learn mène à plasticité), Tinker (théorique), Weimerskirch (only suggest memory)*] *[courbin = switch souvent possiblement avec learn, Zango = suggère, Woo = suggère, Estes = suggère.]*

*Wilson-Rankin: Because resources and their distribution vary both in time and space, foraging strategies must allow for the detection and response to fluctuations in resource levels* (Ishii et Shimada : learning = plasticity)

A number of long-term studies observed that generalist and specialist individuals can achieve similar fitness [sources: à partir de Woo]. An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc, Courbin, Chang]. The resource-predictability hypothesis advances that when resources are predictable, particularly on short time-scales, individual specialists should benefit from higher fitness returns. The rationale is that individuals should have higher prey delivery rates when they repeatedly employ the same foraging technique, as it is easier to assess prey predictability over shorter time-scales. In contrast, individual generalists should be advantaged over longer time scales, as resource parameters are expected to fluctuate. [revoir ceia et ramos pour les sources]
*ce qu'il manque, c'est qu'on a aucune idée comment des différences individuelles de variabilité environnementale se traduisent par des différences de stratégies*
